Higher-Order unification for free!

### 2024-04-13 paper/main.tex
sec 3.5 with spellchecker + some todo

First and foremost problematic terms stored in
\linkStore have to be moved back into the game:
a suspended link must be turned into a valid assignment.
This operation is possible thanks to \fullref{inv:linklhs},
thanks to the fact that no link causes an occur-check~(\ref{sec:oc})
and the fact that \linkStore is duplicate free (\cref{TODO}).

The second step amounts at allocating new variables in the
memory of \Fo{}. This technicality is required because some
higher-order unification may need to prune a variable. For example
$F\appsep x\appsep y = F\appsep x\appsep z$ requires to allocate a 
variable $G$ in order to express the assignment $F_{ab} \mapsto G_a$.

The last step amounts at decompiling each assignment.
Decompiling a term is trivial since \mapStore is a bijection.
The only tricky part concerns the \elpiIn{abs} node. In out simple setting
the \elpiIn{flam} node carries no extra info (other then the function body),
so each \elpiIn{abs} node can be trivially converted to a \elpiIn{flam} one.
In the case of CIC, where lambdas carry the type of the bound variable, one
has to store it somewhere. Note how this piece of information is akin
to the arity of variables, that is CIC's unification variables have a
(function) type, and that type can be used to annotate the lambdas
needed in order to express their assignment.

\begin{lemma}[Compilation round trip]\label{prop:comprt} If
  \elpiIn{compile S T [] M [] _ [] _} then \elpiIn{decompile M T S}
\end{lemma}
% \begin{proof}[Proof sketch]
% Trivial since \mapStore is a bijection and 
% the terms are beta normal.
% some discussion about commit maybellam to be done later.
% \end{proof}

@@

\begin{theorem}[Fidelity in \maybeeta]
  % F x = z, F x y = z y
  Given a list of unification problems \foUnifPb, such that \noteD{riprendere sec 3.1}
  $\forall t, t\in\subterm{\foUnifPb} \land t \notin \notllambda$, \noteD{dire che M e biiettivo}
  the introduction 
  of \linketa guarantees \fullref{prop:fidelity}.
  \footnote{We also suppose that any higher-order variable is always applied with
  the same number of arguments. This problem is addressed in \cref{sec:invariant1}}\noteD{modificare accordingly}
  \label{lemma:fidelity-maybeeta}
\end{theorem}

>>>>

First and foremost, problematic terms stored in
\linkStore have to be moved back into the game:
a suspended link must be turned into a valid assignment.
This operation is possible thanks to \fullref{inv:linklhs},
which ensures that no link causes an occur-check~(\ref{sec:oc})
and the fact that \linkStore is duplicate-free (\cref{TODO}).

The second step involves allocating new variables in the
memory of \Fo{}. This technicality is required because some
higher-order unifications may require pruning a variable. For example,
$F\appsep x\appsep y = F\appsep x\appsep z$ requires allocating a 
variable $G$ in order to express the assignment $F_{ab} \mapsto G_a$.

The final step is to decompile each assignment.
Decompiling a term is straightforward since \mapStore is a bijection.
The only complex part concerns the \elpiIn{abs} node. In our simple setting,
the \elpiIn{flam} node carries no additional information (other than the function body),
so each \elpiIn{abs} node can be trivially converted to a \elpiIn{flam} one.
However, in the case of CIC, where lambdas carry the type of the bound variable, one
must store this information somewhere. Note that this information is similar
to the arity of variables; that in CIC, unification variables have a
(function) type, and this type can be used to annotate the lambdas
needed to express their assignment.

\begin{lemma}[Compilation round trip]\label{prop:comprt} If
  \elpiIn{compile S T [] M [] _ [] _} then \elpiIn{decompile M T S}
\end{lemma}\noteD{Should also decompile links\dots}
% \begin{proof}[Proof sketch]
% Trivial since \mapStore is a bijection and 
% the terms are beta normal.
% some discussion about commit maybellam to be done later.
% \end{proof}

@@

\begin{theorem}[Fidelity in \maybeeta]
  % F x = z, F x y = z y
  Given a list of unification problems \foUnifPb, such that \noteD{riprendere sec 3.1}
  $\forall t, t\in\subterm{\foUnifPb} \land t \notin \notllambda$ and the 
  map memory is bijective,
  the introduction 
  of \linketa guarantees \fullref{prop:fidelity}.
  \footnote{A map memory is bijective if any higher-order variable is applied
  with the same number of arguments. This problem is addressed in
  \cref{sec:invariant1}}
  \label{lemma:fidelity-maybeeta}
\end{theorem}
